LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems

### 2025-07-31 docs/paper/appendix.tex
feat: update paper

\subsection{Installation}
\OS{Ernesto, can we organise this in a better order?}
The recommended way to install \pylucid is via the \texttt{pip} package manager, using one of the pre-built wheels, 
hence avoiding the time-consuming need to compile the code from source.
Provided \texttt{Python>=3.8} is already present, installing \pylucid requires only the command
\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
pip install pylucid[gui,plot] --index-url \
  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
\end{lstlisting}
If the desired platform's wheel is not available, \pylucid can be installed from source by cloning the repository and running
\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
pip install .[gui,plot]
\end{lstlisting}
Note that this requires \texttt{Python>=3.8} and \texttt{Bazel>=8.0} to be installed on the system.
For more details on the installation process, please refer to the online documentation at \url{https://lucidtoolsource.gitlab.io/lucid/md_docs_2Pylucid.html}.

@@

\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~[\ref{fig:gui-left},\ref{fig:gui-right}], while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
\begin{figure}
    \centering
    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
    }
    \label{fig:gui-left}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
    The right half of the screen shows the results produced by \lucid, including a plot of the computed barrier function, 
    the numerical safety guarantee and , and detailed logs of the computations.
    }
    \label{fig:gui-right}
\end{figure}

>>>>

\subsection{Installation}
\OS{Ernesto, can we organise this in a better order?}
The recommended way to install \pylucid is via the \texttt{pip} package manager, using one of the pre-built wheels, 
hence avoiding the time-consuming need to compile the code from source.
Provided \texttt{Python>=3.8} is already present, installing \pylucid requires only the command
\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
pip install "pylucid[gui,plot]" --index-url \
  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
\end{lstlisting}
If the desired platform's wheel is not available, \pylucid can be installed from source running the following commands:
\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
git clone https://gitlab.com/lucidtoolsource/lucid.git
cd lucid
pip install .[gui,plot]
\end{lstlisting}
Note that this requires \texttt{Python>=3.8} and \texttt{Bazel>=8.0} to be installed on the system.
For more details on the installation process, please refer to the online documentation at \url{https://lucidtoolsource.gitlab.io/lucid/md_docs_2Pylucid.html}.

@@

\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~\ref{fig:gui-left}--\ref{fig:gui-right}, while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
\begin{figure}
    \centering
    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
    }
    \label{fig:gui-left}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
    The right half of the screen shows the results produced by \lucid, including a plot of the computed barrier function, 
    the numerical safety guarantee and , and detailed logs of the computations.
    }
    \label{fig:gui-right}
\end{figure}

### 2025-07-31 docs/paper/figures/architecture.tex
feat: update paper

        % Lucid blocks
        \node[block, below=1cm of input] (estimator) {\Circled{2} Estimator};
        \node[block, right=of estimator] (tuner) {\Circled{3} Tuner};
        \node[block, left=of estimator] (sets) {\Circled{1} Safety Specification};
        \node[block, below=of estimator] (feature) {\Circled{4} Feature Map}; % / Barrier template
        \node[block, left=of feature] (optimizer) {\Circled{5} Solver};
        % \node[block, below=of optimizer] (verifier) {Verifier};
        \node[draw, dashed, inner sep=0.25cm, rounded corners,
        % fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{\lucid}}] {};

>>>>

        % Lucid blocks
        \node[block, below=1cm of input] (estimator) {\Circled{2} Estimator};
        \node[block, right=of estimator] (tuner) {\Circled{3} Tuner};
        \node[block, left=of estimator] (sets) {\Circled{1} Safety Specification};
        \node[block, below=of estimator, text width=2.4cm] (feature) {\Circled{4} Feature Map}; % / Barrier template
        \node[block, left=.4cm of feature] (optimizer) {\Circled{5} Solver};
        % \node[block, below=of optimizer] (verifier) {Verifier};
        \node[draw, dashed, inner sep=0.25cm, rounded corners,
        % fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{\lucid}}] {};
